### 2015-03-17 Kokkos_PG_Subviews.tex
Subviews: Minor formatting and wording changes

After reading this chapter, you should understand the following:
\begin{itemize}
\item A \emph{slice} of a multidimensional array behaves as an array,
  and is a view of a structured subset of that array
\item A \emph{subview} is a slice of an existing Kokkos View
\item A subview has the same reference count as their parent View
\item Use C++11 \texttt{auto} to let Kokkos pick the subview's type
\end{itemize}

@@

A \emph{slice} of a multidimensional array behaves as an array, and is
a view of a structured subset of the original array.  ``Behaves as an
array'' means that the slice has the same syntax as an array should;
one can access its entries using array indexing notation.  ``View''
means that the slice and the original array point to the same data.
That is, the slice sees changes to the original array, and vice versa.
``Structured subset'' means a cross product of indices along each
dimension, as for example a plane or face of a cube.  If the original
array has dimensions $(N_0, N_1, \dots, N_{k-1})$, then a slice views
all entries whose indices are $(\alpha_0, \alpha_1, \dots,
\alpha_{k-1})$, where $\alpha_j$ is a subset of $[0, 1, \dots,
N_j-1]$.

@@

In Kokkos, a \emph{subview} is a slice of a View.  A subview has the
same reference count as its parent View, so the parent View won't be
deallocated before all subviews go away.

@@

To take a subview of a View, use the \texttt{subview} function.  This
function is overloaded for all different kinds of Views and index
ranges.  For example, the following is equivalent to the above example
\texttt{A(2:4, 3:7)}:

\begin{lstlisting}
const size_t N0 = ...;
const size_t N1 = ...;
View<double**> A ("A", N0, N1);

auto A_sub = 
  subview (A, std::make_pair (2, 4), std::make_pair (3, 7));
\end{lstlisting}

The Kokkos equivalent of a contiguous index range \texttt{3:7} is
\\ \lstinline!std::pair<size_t, size_t>(3, 7)!.  The Kokkos equivalent of
\texttt{:} (a colon by itself; the whole index range for that
dimension) is \texttt{ALL()} (an instance of the \texttt{Kokkos::ALL}
class).  Kokkos does not currently have equivalents of the strided or
arbitrary index sets.

Every subview is also a View.  This means that you may take a subview
of a subview.

@@

Given a View with $k$ dimensions, we call that View \emph{degenerate}
if any of those dimensions is zero.  Degenerate Views are useful for
keeping code simple, by avoiding special cases.  For example, in an
MPI (Message-Passing Interface) distributed-memory parallel code that
uses Kokkos to represent local (per-process) data structures,

>>>>

After reading this chapter, you should understand the following:
\begin{itemize}
\item A \emph{slice} of a multidimensional array behaves as an array,
  and is a view of a structured subset of that array
\item A \emph{subview} is a slice of an existing Kokkos View
\item A subview has the same reference count as its parent View
\item Use C++11 type inference (\lstinline!auto!) to let Kokkos pick the subview's type
\end{itemize}

@@

In Kokkos, a \emph{subview} is a slice of a View.  A \emph{slice} of a
multidimensional array behaves as an array, and is a view of a
structured subset of the original array.  ``Behaves as an array''
means that the slice has the same syntax as an array should; one can
access its entries using array indexing notation.  ``View'' means that
the slice and the original array point to the same data.  That is, the
slice sees changes to the original array, and vice versa.
``Structured subset'' means a cross product of indices along each
dimension, as for example a plane or face of a cube.  If the original
array has dimensions $(N_0, N_1, \dots, N_{k-1})$, then a slice views
all entries whose indices are $(\alpha_0, \alpha_1, \dots,
\alpha_{k-1})$, where $\alpha_j$ is an ordered subset of $\{0, 1,
\dots, N_j-1\}$.

@@

@@

To take a subview of a View, use the \texttt{Kokkos::subview}
function.  This function is overloaded for all different kinds of
Views and index ranges.  For example, the following code is equivalent
to the above example \texttt{A(2:4, 3:7)}:
%%
\begin{lstlisting}
const size_t N0 = ...;
const size_t N1 = ...;
View<double**> A ("A", N0, N1);

auto A_sub = subview (A, make_pair (2, 4), make_pair (3, 7));
\end{lstlisting}
%
In the above example and those that follow in this chapter, 
we assume that \lstinline!Kokkos::View!, \lstinline!Kokkos::subview!,
\lstinline!Kokkos::ALL!, \lstinline!std::make_pair!, and \lstinline!std::pair!
have been imported into the working C++ namespace.

The Kokkos equivalent of a contiguous index range \texttt{3:7} is \\
\lstinline!pair<size_t, size_t>(3, 7)!.  The Kokkos equivalent of
\texttt{:} (a colon by itself; the whole index range for that
dimension) is \texttt{ALL()} (an instance of the \texttt{ALL} class,
which Kokkos uses only for this purpose).  Kokkos does not currently
have equivalents of the strided or arbitrary index sets.

A subview has the same reference count as its parent View, so the
parent View won't be deallocated before all subviews go away.  Every
subview is also a View.  This means that you may take a subview of a
subview.

@@

Given a View with $k$ dimensions, we call that View \emph{degenerate}
if any of those dimensions is zero.  Degenerate Views are useful for
keeping code simple, by avoiding special cases.  For example, consider
a MPI (Message-Passing Interface) distributed-memory parallel code
that uses Kokkos to represent local (per-process) data structures.
Suppose that the code distributes a dense matrix (2-D array) in block
row fashion over the MPI processes in a communicator.  It could be
that some processes own zero rows of the matrix.  This may not be
efficient, since those processes do no work yet participate in
collectives, but it might be possible.  In this case, allowing Views
with zero rows would reduce the number of special cases in the code.
